Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-05 gibbs.tex
Update gibbs.tex

Although the salinity during compression in \emph{open} system remains constant, the number of ions in a compression volume, \ie in the volume where the gel is compressed (or swells), changes.
%As the compression volume $\Vbox$ we chose the volume of the free swelling equilibrium state of the gel, $\Vbox = \Vgel^0$.
In the Figure \ref{fig: NV} we depicted the number of $\cl$ ions in the volume $\Vbox$, calculated per unit volume, $\ncl =$ $\Ncl/\Vbox$, as a function of the gel molar volume. 
The depicted value can be considered as the density of $\cl$ ions averaged out over the compression volume $\Vbox$.

As expected in the case of closed system compression these dependencies look like horizontal lines, whereas in an open system, the amount of ions in compression volume increases with compression. 
This implies, that the compression of the gel in the open system pulls out the ions from the bath to the compression volume, $\Vbox$. 
And vice versa, the swelling of the gel pushes ions out to the bath.

Finally, in Figure \ref{fig: CN} the same processes are depicted in coordinates $\ncl$ --- $\cs$. 
In these coordinates, both ways of the compression, in \emph{open} and in \emph{closed} system, appear as straight vertical and horizontal lines correspondingly.

In our study, we modeled the compression of the gel in equilibrium with reservoirs of 40 different salinities, ranging from 0.001 to 0.5 mol/l. 
Every open system compression resulted in a defined free swelling equilibrium state, which we used as the initial ones for the compression in closed systems. 
All the corresponding dependencies are depicted in Figures~\ref{fig: PV and CV} and \ref{fig: NV and CN} as thin grey dashed lines (some of them are highlighted and colored).
The states corresponding to $P^{gel}=0$, 5 and 10 bar pressure are marked by open circles, squares, and crosses respectively. 
The non-shadowed areas in the Figures highlight the states in which the gel partial pressure ranges between 0 and 5 bar.

>>>>

Although the salinity during compression in \emph{open system} remains constant, the amount of ions in the compressed subsystem (\ie in the volume where the gel is compressed (or swells)), changes.
Here, the compression volume $\Vbox$ is the volume of the \emph{free swelling equilibrium} state of the gel, $\Vbox = \Vgel^0$.
Figure \ref{fig: NV} shows number of $\cl$ ions in the volume $\Vbox$ per unit volume, $\ncl =$ $\Ncl/\Vbox$, as a function of the gel molar volume. 
The depicted values can be considered as the average density of $\cl$ ions in the compression volume $\Vbox$.

The $\ncl$-$\Vgel$ dependencies look like horizontal lines in the case of \emph{closed system} compression,
whereas $\ncl$ increases with $\Vgel$ during the compression in the \emph{open system} case. 
This implies, that the compression of the gel in the \emph{open system} pulls out the ions from the bath to the compression volume, $\Vbox$. 
And vice versa, the swelling of the gel pushes ions out to the bath.

Finally, the same processes are depicted in Figure \ref{fig: CN} in coordinates $\ncl$ --- $\cs$. 
In these coordinates, both ways of the compression, in \emph{open} and in \emph{closed} systems, appear as straight vertical and horizontal lines correspondingly.

In our study, we modeled the compression of the gel in equilibrium with reservoirs of 40 different salinities, ranging from 0.001 to 0.5 mol/l. 
The \emph{open system} compressions resulted in a defined free swelling equilibrium states,
which we used as the initial conditions for the respective compressions in \emph{closed systems}. 
All the corresponding dependencies are depicted in Figures~\ref{fig: PV and CV} and \ref{fig: NV and CN} as thin grey dashed lines (some of them are highlighted and colored).
The states corresponding to $P^{gel}=0$, 5 and 10 bar pressure are marked by open circles, squares, and crosses respectively. 
The non-shadowed areas in the Figures highlight the states in which the gel partial pressure ranges between the experimentally relevant values, 0 and 5 bar.
